Color- and piece-blind chess

### 2019-03-09 trunk/chess/papers/blind.tex
Implemented spycheck (not tested)

There is one subtlety here, which is that we can't fairly use the
information of the actual side-to-move, as above. So there is some
additional chance that we end up making a dumb move because we
both mispredicted the side-to-move and the identity of some pieces.

@@

@@

- Other structures for the network
- Stochastic approach
- How do the solutions compare to other chess algorithms that
  could be applied in the blind? Random works, also lexicographic,
  any others? Most are inspecting the board state, obviously.
- Could estimate the upper bound for accuracy by blinding every
  game in the database, and doing a ``lookup''-based version of
  the eval.

>>>>

There is one subtlety here. Above we argued that it was safe to use
the actual side-to-move instead of the predicted one; but here it
would not be equivalent to do so. Instead, we first prioritize all
apparent spy-check moves where the predicted source piece matches the
predicted side-to-move, then we try the opposite. (Ties are broken by
preferring to capture with a lower-value predicted piece, and then
randomly.) Due to this, there is some additional chance that we end up
making an especially dumb move because we both mispredicted the
side-to-move and the identity of some pieces.

@@

\subsection{Future work}

The predicted board often expresses uncertainty about some squares,
which could be thought of as probabilities. A principled improvement
would be to try to find moves that are good in expectation, that is,
integrated all possible boards in proportion to their predicted
probability. A good approximation might be had by sampling a bunch
of boards according to the predicted distribution, and then using
Stockfish to score the top $k$ moves for each; we can then order
moves by their expected score. Unfortunately, it is not easy to
efficiently get Stockfish to generate scored moves for $k \neq 1$.
Even with $k = 1$, this approach would be slow, taking about a
second for each (distinct) sampled board. So I did not try it,
at least not before submitting this paper.

@@

- Other structures for the network
- How do the solutions compare to other chess algorithms that
  could be applied in the blind? Random works, also lexicographic,
  any others? Most are inspecting the board state, obviously.
- Could estimate the upper bound for accuracy by blinding every
  game in the database, and doing a ``lookup''-based version of
  the eval.
